---
title: "Hackathon Project Task 1"
author: "Xiaohan (Julia) Wu"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
---
  
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

<!-- Do not forget to input your Github username in the YAML configuration up there --> juliawuxh

***

```{r, include = T}
library(tidyverse)
library(gt)
library(gtExtras)
library(dplyr)
library(ggplot2)
library(haven)
```

<br>

### Task 1.4 - Perceived hatefulness of social media post

Create a gt/gtExtras table that reports the aggregated perceived hatefulness of a set of social media posts, following good practice of visualization. For this task, consider the following:

1. Some guidance for the data preparation:
 - The content of the social media posts is stored in two types of variables:
vig_{x}_topic and vig_{x}_sender_message. Every respondent evaluated 8 different messages, which is why x goes from 1 to 8. The perception of hatefulness is stored in the variables vig_{x}_hateful.
 - Drop observations where vig_1_hateful is missing.
 - Recode the vig_{x}_topic variables according to the following scheme:
gender = "Women", ideologydems = "Democrats", ideologyreps = "Republicans", muslim = "Muslim immigrants".
 - Construct the full content of the message by pasting together the strings
of the recoded vig_{x}_topic and vig_{x}_sender_message variables. For instance, one of the full messages reads: “Republicans should be stopped from spreading falsehoods.”
 - For the evaluation, you should average across all evaluated vignettes across all responses, i.e. your unit of analysis is vignettes, not respondents.

2. Your table should contain the following information: (1) The message text, (2) the mean and standard deviation of the hatefulness rating by message, and (3) a barplot displaying the distribution of hatefulness ratings 1 to 5 per message.

3. The average hatefulness column should be colored by value.

4. The table should provide a meaningful title and description, making it a
standalone product that speaks for itself.

```{r}
# Load the RDS file containing survey data
meof_usa_survey_df <- readRDS("~/Hackathon proj individual/survey/meof_usa_survey_df.RDS")
# Create a new dataframe
df <- meof_usa_survey_df
# Display the first few rows to check
head(df)
```
#### Step 1: Data preparation
```{r}
df <- df %>%
  drop_na(vig_1_hateful) # Drop NA for vig_1_hateful

# Initialize an empty dataframe for results
result_df <- data.frame(message_text = character(), hateful_rating = integer(), stringsAsFactors = FALSE)

# Loop through vig_1 to vig_8
for (x in 1:8) {
  # Create dynamic column names for topic, sender message, and hateful columns
  topic_column <- sym(paste("vig_", x, "_topic", sep = ""))
  sender_message_column <- sym(paste("vig_", x, "_sender_message", sep = ""))
  hateful_column <- sym(paste("vig_", x, "_hateful", sep = ""))
  
  # Recode the topic column and put into message_text column 
  df <- df %>%
    mutate( 
      !!topic_column := recode(!!topic_column,
        "gender" = "Women",
        "ideologydems" = "Democrats",
        "ideologyreps" = "Republicans",
        "muslim" = "Muslim immigrants"
      ),
      message_text = paste(!!topic_column, !!sender_message_column, sep = " ")
    )
  
  # Create a temporary dataframe with personid, message_text, and hateful_rating
  result_df <- df %>%
    select(message_text, hateful_rating = !!sym(hateful_column)) %>%
    filter(!is.na(hateful_rating))  # Remove rows with NA in hateful_rating column
}

# Print the result dataframe
head(result_df)

# Sanity check so far
# df$message_text
# df$vig_8_topic
# df$vig_1_sender_message
```

#### Step 2: Calculate the average hatefulness for each unique message_text
```{r}
# Calculate the average hateful rating and standard deviation for each unique message_text
result_df <- result_df %>%
  group_by(message_text) %>%
  reframe(
    hateful_rating = hateful_rating,
    avg_hateful_rating = mean(hateful_rating, na.rm = TRUE),
    std_hateful_rating = sd(hateful_rating, na.rm = TRUE)
  ) 

# Print the evaluation_df
head(result_df)
```
#### Step 3: Create the gt table
```{r}
# Create gt table
gt_table <- result_df %>%
  group_by(message_text) %>%
  reframe( 
    message_text = message_text,
    hateful_rating = list(hateful_rating),
    avg_hateful_rating = as.numeric(avg_hateful_rating),
    std_hateful_rating = as.numeric(std_hateful_rating)
  ) %>%
  distinct() %>% # Remove duplicates for message_text
  rename( # Rename column for better visual
    "Message" = message_text,
    "Average Rating" = avg_hateful_rating,
    "Standard Deviation" = std_hateful_rating,
    "Hateful Rating" = hateful_rating
  ) %>%
  gt() %>%
  gt_theme_espn() %>%
  tab_header(
    title = "Aggregated Perceived Hatefulness of Social Media Posts",
    subtitle = "This table displays the average and standard deviation of hatefulness ratings by survey participants for each unique message. The ratings range from 1 - 'Not hateful at all' to 5 - 'Extremely Hateful'"
  ) %>%
  fmt_number( # Format numerical columns with 2 decimals
    columns = c("Average Rating", "Standard Deviation"),
    decimals = 2
  ) %>%
  tab_spanner( # Group ratings under spanner
    label = "1|2|3|4|5",
    columns = "Hateful Rating"
  ) %>%
  gt_plt_dist( # Add histograms of ratings
    "Hateful Rating",
    type = "histogram",
    fig_dim = c(10,30),
    line_color = "black",
    fill_color = "grey",
    bw = 1
  ) %>%
  data_color( # Color data based on Average Rating
    columns = "Average Rating",
    target_columns = "Average Rating",
    palette = c("yellow", "red")
  ) %>%
  tab_source_note(md("Data source: The Media Exposure and Opinion Formation (MEOF) study - USA. The vignette experiment was conducted in 2019.")) 

# Print the gt table
gt_table
```